% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}
\usepackage{enumitem} %for lists within experience section

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{9pt}{9pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

\newenvironment{jobshort}[2]
  {%
    % Line 1: Job Position (left) and Period (right)
    \noindent\textbf{#1} \hfill #2 \par
    % \vspace{1pt} % A small vertical space before the list
    % Start a compact itemize list for the work experience
    \begin{itemize}[nosep, leftmargin=1.5em, itemsep=2pt, label=$\bullet$]
  }
  {%
    % End the list
    \end{itemize}
  }

\newenvironment{joblong}[2]
    {
    \begin{tabularx}{\linewidth}{@{}l X r@{}}
    \textbf{#1} & \hfill &  #2 \\[1pt]
    \end{tabularx}
    \begin{itemize}[nosep, after=\strut, leftmargin=1em, itemsep=3pt, label=--]
    }
    {
    \end{itemize}
    }
    
% project environment
\newenvironment{project}[2]
  {
    % Line 1: Project Title (left) and Tech Stack (right)
    \noindent\textbf{#1} \hfill \textit{#2}\\[2pt] % Use \\ instead of \par
  }
  {
    % \vspace{\topsep} % Adds a tiny, consistent space after the project
  }

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Abhishek Prasad} \\[7.5pt]
\href{https://github.com/abhishek622}{\raisebox{-0.05\height}\faGithub\ abhishek622} \ $|$ \ 
\href{https://linkedin.com/in/abhishekprasad00}{\raisebox{-0.05\height}\faLinkedin\ abhishekprasad00} \ $|$ \ 
\href{mailto:application.aprasad@gmail.com}{\raisebox{-0.05\height}\faEnvelope\ application.aprasad@gmail.com} \ $|$ \ 
\href{https://portfolio.abhishekprasad0602.workers.dev}{\raisebox{-0.05\height}\faGlobe\ portfolio} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% SUMMARY PARAGRAPH
%----------------------------------------------------------------------------------------

Backend Developer with experience building and shipping production-grade features in a global SaaS environment. Adept at taking full ownership of projects, delivering with discipline, and solving impactful problems to drive business growth.

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTIONS
%----------------------------------------------------------------------------------------

%Experience
\section{Work Experience}

\begin{jobshort}
 {Backend Developer - Ringover}                        % job_position
  {June 2023 -- Present}                    % period
   \item Collaborated with cross-functional teams to develop key features and resolve issues in services built within a distributed monolith using \textbf{node.js}, ensuring high performance, scalability, and reliability for over 10k+ active users.
\item Owned end-to-end integration of 4 enterprise CRMs (Sellsy, Odoo, Dynamics 365, Vincere) — expanding Cadence’s ecosystem by \textbf{40\%} with two-way sync, real-time logs, and socket-based bulk imports.
\item Independently developed a rate-limited public API to enable client-side automation, featuring asynchronous bulk lead importing (1,000+ per request) and management of over 100 lead tasks.
\end{jobshort}

\begin{jobshort}
  {Backend Developer Intern - Ringover}               % job_position
  {July 2022 -- May 2023}                  % period
  % {Ringover}                               % company_name
  % {Remote}                                 % location
   \item Developed global settings with user-defined timezones, using RabbitMQ and cron-based scheduler to ensure client outreach occurred at optimal local times — maximizing sales opportunities.
    \item Built the "Cadence Support Tool" using node.js and TiDB(Open-source, distributed SQL database) to give the support team secure data access, slashing routine ticket volume and accelerating issue resolution.
\end{jobshort}

\begin{jobshort}
  {Project Intern - HighRadius}                        % job_position
  {Jan 2022 -- Apr 2022}                  % period
  % {HighRadius}                            % company_name
  % {Remote}                                % location
   \item Developed AI-powered fintech B2B cloud application — cash flow forecasting engine with Flask ML + Java backend achieving 89\% accuracy.
\item Designed efficient invoice search system with MySQL optimizations and React UI — with average load time of 0.3s for 50K+ records.
\end{jobshort}
  
%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{project}
    {\href{https://github.com/abhishek622/gomind}{Gomind - AI-Powered Go CLI Task Manager \raisebox{-0.05\height}\faGithub}}
    {Go, Awan LLM, MongoDB}
    Built a CLI tool that takes input in natural language and uses AI to auto-generate detailed tasks with MongoDB persistence. Designed for developers to keep quick notes through intelligent task management.
\end{project}

\begin{project}
    {\href{https://github.com/abhishek622/movieapp}{MovieApp - Microservices Architecture \raisebox{-0.05\height}\faGithub}}
    {Go, MySQL, Docker, gRPC}
    Movie platform backend built with observability, scalability, and resilience in mind. Features comprehensive monitoring with Prometheus/Grafana, service discovery, caching with Redis, and distributed tracing for performance and reliability.
\end{project}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X r@{}}
\textbf{Institute of Technical Education and Research} && Bhubaneswar, India  \\
B.Tech in Computer Science and Engineering - CGPA: 8.66/10.0 && June 2019 -- May 2023
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Languages: & Javascript, Go, Python, SQL \\
Tools and Frameworks: & Node.js, Gin, Git, Docker, GCP, Bitbucket, GenAI, VS Code \\
% Databases &  MySQL, PostgreSQL, MongoDB, Redis \\
% Infrastructure & Docker, Kubernetes, Redis, RabbitMQ, Prometheus \\
\end{tabularx}

\end{document}